Music Perception 2020: Stimuli profiles

### 2020-10-11 material/stimuli/R/analysis/ioi.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Tempo Analysis: The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a summary of all analyses for a tempo.

>>>>

---
title: 'Music Perception 2020: Stimuli profiles'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
